---
title: "Home_Work_2"
author: "Zebosi Brian, Zhengqiang Ni, Ruina Chang"
date: "9/20/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Question_1

a). Plot a histogram of the variable growth_rate

```{r}
library(fishdata)
juvenile.df <- juvenile_metrics
hist(juvenile.df$growth_rate)
```



Growth data doesn't seem to be normally distributed. i.e. data tends be skewed to slightly skewed. 


b). Use the function ks.test in R to test a normality

```{r}
ks.test(juvenile.df$growth_rate, 'pnorm', 
        mean(juvenile.df$growth_rate), 
        sd(juvenile.df$growth_rate))
```

p-value = 0.00785, reject the null hypothesis that the growth rate data follows a normal distribution. 

i.e. Accept the alternative hypothesis that growth rate data doesnot follow a normal distribution. 


c). 

```{r}
growth.log <- log(juvenile.df$growth_rate)

t.test(growth.log, mu = 1.7)
```


```{r}
exp(1.7-(mean(growth.log)))
```
growth rate is 3.2 times less than median growth rate. 



###  Question_2

a)

```{r}
bw.df <- read.csv("Birthweight_reduced_kg_R.csv")
```




```{r}
boxplot(Birthweight~smoker, data=bw.df)
```


T-test using calculated manaully

```{r}
m1 <- length(bw.df$Birthweight[bw.df$smoker == 1])
m2 <- length(bw.df$Birthweight[bw.df$smoker == 0])
s2 <- var(bw.df$Birthweight[bw.df$smoker == 0])
s1 <- var(bw.df$Birthweight[bw.df$smoker == 1])
Sp2 <- (s1+s2)/2
test.stat <- (mean(bw.df$Birthweight[bw.df$smoker == 1])-
                (mean(bw.df$Birthweight[bw.df$smoker == 0])))/sqrt(Sp2*(1/m1+1/m2))

test.stat
y <- ((m1+m2)-2)
2*(1-pt(abs(test.stat), y))
```

T-test using R t.test function

```{r}
t.test(bw.df$Birthweight[bw.df$smoker == 0], bw.df$Birthweight[bw.df$smoker == 1], 
       conf.level = 0.90, alternative = "two.sided",var.equal = T)
```

c).

```{r}
mean_diff = mean(bw.df$Birthweight[bw.df$smoker == 0])- (mean(bw.df$Birthweight[bw.df$smoker == 1]))
s.e.m <- sqrt(Sp2*(1/m1+1/m2))
qtn <- abs(qt(0.05,((m1+m2)-2)))
Lower_cl <- mean_diff-(qtn*s.e.m)
Lower_cl
Upper_cl <- mean_diff+(qtn*s.e.m)
Upper_cl

```
manual computation:(0.074 , 0.675) and using R-t.test function (0.0734 , 0.677)


d).


P < 0.05, suggests that there is moderate evidence for difference between mother's smoking habits. 


We are 90% confident that the difference between mother's smoking habits is 0.0734 between 0.677.



## Question_3

```{r}
chol.df <- read.csv("Cholesterol_R.csv")

```

a)

Experimental unit : 18 individuals diagnosed with high cholesterol who replaced butter

Population : individuals diagnosed with high cholesterol who replaced butter

Treatments : margarine [A and B]

Response : blood cholesterol levels

b) 

```{r}
boxplot(After8weeks~Margarine, data = chol.df)
```

C)

Computation of t.test by hand

```{r}
m1 <- length(chol.df$After8weeks[chol.df$Margarine == "A"])
m2 <- length(chol.df$After8weeks[chol.df$Margarine == "B"])
s2 <- var(chol.df$After8weeks[chol.df$Margarine == "A"])
s1 <- var(chol.df$After8weeks[chol.df$Margarine == "B"])
Sp2 <- (s1+s2)/2
test.stat <- (mean(chol.df$After8weeks[chol.df$Margarine == "A"])-
                (mean(chol.df$After8weeks[chol.df$Margarine == "B"])))/sqrt(Sp2*(1/m1+1/m2))

test.stat
```

```{r}
df <- ((m1+m2)-2)
2*(1-pt(abs(test.stat), df))
```


T.test using R_t.test function

```{r}
t.test(chol.df$After8weeks[chol.df$Margarine == "B"], chol.df$After8weeks[chol.df$Margarine == "A"], 
       conf.level = 0.95, alternative = "two.sided",var.equal = T)
```

d)


(-0.5126535,  1.6726535)

e)


P-value > 0.05, there is little or no evidence that there is difference in mean cholesterol reduction 

between the two brands of margarine after 8 weeks of use




### Question_4

```{r}
att.df <- read.csv("attendance.csv")
```

a)

```{r}
boxplot(responses~group, data=att.df)
```

b)

```{r}
par(mfrow=c(1,2))
qqnorm(att.df$responses[att.df$group == 1])
qqline(att.df$responses[att.df$group == 1])
qqnorm(att.df$responses[att.df$group == 0])
qqline(att.df$responses[att.df$group == 0])
```


Plots of the data look close to random samples from a normal distribution.

seem normally distributed. 




c).

```{r}
par(mfrow=c(1,2))
acf(att.df$responses[att.df$group == 1], main="Group_1")
acf(att.df$responses[att.df$group == 0], main="Group_0")
```




d)


T.test wouldn't adequately account for the variation because there is correlation between points i.e. 

Assumption of independence is violated. 




### Question_5

```{r}
grad.df <- read.csv("grades.csv")
```


a)


```{r}
boxplot(grades~class, data=grad.df)
```


b)


```{r}
par(mfrow=c(2,2))
qqnorm(grad.df$grades[grad.df$class== 1])
qqline(grad.df$grades[grad.df$class== 1])
qqnorm(grad.df$grades[grad.df$class== 0])
qqline(grad.df$grades[grad.df$class== 0])
hist(grad.df$grades[grad.df$class== 1], xlab="Class",main="Class_1")
hist(grad.df$grades[grad.df$class== 0], xlab="Class",main="Class_0")
```



c)


```{r}
grad.df$log_grades <- log(grad.df$grades)
par(mfrow=c(2,2))
qqnorm(grad.df$log_grades[grad.df$class== 1])
qqline(grad.df$log_grades[grad.df$class== 1])
qqnorm(grad.df$log_grades[grad.df$class== 0])
qqline(grad.df$log_grades[grad.df$class== 0])
hist(grad.df$log_grades[grad.df$class== 1], xlab="Class",main="Class_1")
hist(grad.df$log_grades[grad.df$class== 0], xlab="Class",main="Class_0")
```





c)

log transformation of grades didn't improve the normality of the grades. 


d)

```{r}
wilcox.test(grad.df$grades[grad.df$class == 1], grad.df$grades[grad.df$class == 0],
            conf.level = 0.9, alternative = "two.sided")
```


